\documentclass{llncs}

%\usepackage{llncsdoc}

%\usepackage{makeidx}  % allows for indexgeneration
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{multirow}

\usepackage{url}
\usepackage{rotating}

%%%Math
\usepackage{latexsym}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsthm}
%\usepackage{eurosans}

\usepackage{eurosym}

\usepackage{longtable}

\usepackage{listings}

\usepackage{color}
\usepackage{textcomp}
\usepackage{achicago}


\definecolor{gray}{gray}{0.5}
\definecolor{green}{rgb}{0,0.5,0}


\begin{document}

\title{Towards a semantic-based representation and computation of quantitative indexes for quality management of requirements.\thanks{The research leading to these results has received funding from the ARTEMIS Joint Undertaking under
grant agreement No 332830-CRYSTAL (CRitical sYSTem engineering AcceLeration project) and from specific national programs and/or funding authorities. This work has been supported by the Spanish Ministry of Industry.}}

\author{Jose Mar\'{i}a \'{A}lvarez-Rodr\'{i}guez\inst{1} \and Juan Llorens\inst{1}  \and Manuela Alejandres\inst{1} \and Jose Fuentes\inst{2}}


\authorrunning{Jose Mar\'{i}a Alvarez \and Juan Llorens\inst{1}  \and Manuela Alejandres\inst{1} \and Jose Fuentes\inst{2}}


\institute{Department of Computer Science, Carlos III University of Madrid, \\ 28911, Leganés, Madrid, Spain\\
  \email{{\{josemaria.alvarez,juan.llorens,manuela.alejandres\}@uc3m.es}}\\
\and The Reuse Company Inc., \\28911, Leganés, Madrid, Spain \\
  \email{{jose.fuentes@reusecompany.es}}\\  
}


\date{}

\maketitle

\renewcommand{\labelitemi}{$\bullet$}
\small
\begin{abstract}
Quality management of requirements has seen a dramatic increase of the amount of 
applications, management platforms, data, etc. gaining momentum in the Systems 
Engineering area and more specifically in the deployment of the next wave of 
critical system. In this context, one of the next big things lies in the 
creation of quality functions that can automatically detect and make decisions 
according to natural-language based requirements specifications and models. In 
this sense quality indicator of requirements seeks for providing an intelligent 
environment for detecting values of such as correctness, consistency and completeness 
based on domain knowledge in which both functional and non-functional properties 
of system components can be validated and verified easing the transition to a 
smart system environment. Thus the testing of critical systems based on 
requirements quality can be seen as a special kind of policy-making strategy 
that must compile several key indicators to summarize data and information and 
obtain an objective quantitative measure. Nevertheless the quantitative analysis 
of several quality indicators is becoming a challenging task due to natural 
language ambiguities and a tangled/heterogeneous environment of data, providers, 
etc. Existing tools and techniques based on traditional processes of quality 
assessment are preventing a proper use of the new dynamic and data environment 
avoiding more timely, adaptable and flexible (on-demand) quantitative index 
creation and, as a consequence, more accurate decisions. On the other hand, 
semantic-based technologies emerge to provide the adequate building blocks to 
represent domain-knowledge and process data in a flexible fashion using a common 
and shared data model. That is why the present paper introduces a Resource 
Description Framework (RDF) vocabulary to semantically represent and compute 
quantitative indexes as part of the implementation of the Open Services for 
Lifecycle Collaboration initiative (OSLC) Quality Management specification. 
Finally some discussion, conclusions and future work are also outlined.
\end{abstract}
%

 \section{Introduction}
 \input{sections/sect-intro}
 \section{Related Work}
 \input{sections/sect-related-work}
\section{Theoretical modeling of a quantitative composite index}
\input{sections/sect-theoretical-rdfindex}
\section{Discussion}
\input{sections/sect-discussion}
\section{Conclusions and Future Work}
\input{sections/sect-conclusions}

% \section{Acknowledgements}
% This work is part of the FP7 Marie Curie Initial Training Network ``RELATE'' (cod. 264840) and developed in the context 
% of the Workpackage 4 and more specifically under the project ``Quality Management in Service-based Systems and Cloud Applications''. It is 
% also supported by the ROCAS project with code TIN2011-27871, a research project partially funded by the Spanish Ministry of Science and Innovation.


\appendix
\clearpage

\bibliographystyle{achicago}
\bibliography{incose}

\input{sections/sect-bio}

\end{document}

