\normalsize
\begin{longtable}[c]{|l|p{3.5cm}|p{10cm}|} 
\hline 
  \textbf{ID} & \textbf{Type} &  \textbf{Description/Venue}  \\\hline
\endhead
  1&Reviewer&Journal of Computers in industry. (IF: 1.709) \\ \hline
  2&Reviewer& Behaviour \& Information Technology, Taylor \& Francis.  (IF: 0.856) \\ \hline 
  3&Reviewer&Journal of Computers in Human Behavior (IF: 2.293) \\ \hline
  4&Reviewer&Journal of Computing (IF: 0,807, 2012) \\ \hline
  5&Reviewer&Journal of Electrical and Computer Engineering \\ \hline
  6&Reviewer&Special Issue in the journal ``Science of Computer Programming'' (IF: 0.622) \\ \hline
  7&Reviewer&Special Issue in the journal ``Future Generation Computer Systems'' (IF: 1.978) \\ \hline 
  8&Scientific Committee&Journal RISTI \\ \hline 
  9&Reviewer&Journal of ``Expert Systems with Applications'' (IF: 2.203) \\ \hline
  10&Technical Development Editor&Manning Publications Co. \\ \hline
  11&Program Committee&Special Session on ``Engineering Tool Integration for Industrial Automation System Development'' (ETAS 2013) \\ \hline
  12&Program Committee&Special Session on the Web of Data (DATAWEB), PCI2013 \\ \hline
  13&Program Committee&DMoLD'13 – Data Mining on Linked Data Workshop \\ \hline
  14&Scientific Committee&Inernational Conference on Hospitality \& Tourism Marketing (ICOHT 2013) \\ \hline
  15&Reviewer& International Conference on Marketing – Challenging Environment (ICOM 2013) \\ \hline
  16&Member of the Advisory Board &Strategic Approaches for Human Capital Management and Development in a Turbulent Economy. IGI-Global. \\ \hline
  17&Member of the Advisory Board&International Business Strategy and Entrepreneurship: An Information Technology Perspective. IGI-Global. \\ \hline
  18&Reviewer&Journal Current Topics in Medicinal Chemistry (IF: 4.174) \\ \hline
  19&Workshop/SI proposal&Cloud Computing meets Semantics (not-submitted) \\ \hline
  20&Secondment proposal&Secondment to make a stay at KIT \\ \hline
  21&Member&W3C Community Group Best Practises for Multilingual Linked Open Data \\ \hline
  22&RELATE activies&MTSC Prague and HotTopics Workshop attendance \\ \hline
  23&Education&Three-month Greek course (10h/week) \\ \hline
  24&Seminar&Master of Web Engineering, University of Oviedo (6h, May) \\ \hline
  25&Seminar&SEERC about my PhD \\ \hline
  26&Others&presentations, etc. \\ \hline
  \hline
  \caption{Other Research Activities}
  \label{table:other-research-activivies}
\end{longtable}



\normalsize
