\documentclass{llncs}

%\usepackage{llncsdoc}

%\usepackage{makeidx}  % allows for indexgeneration
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{multirow}

\usepackage{url}
\usepackage{rotating}

%%%Math
\usepackage{latexsym}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsthm}
%\usepackage{eurosans}

\usepackage{eurosym}

\usepackage{longtable}

\usepackage{listings}

\usepackage{color}
\usepackage{textcomp}



\definecolor{gray}{gray}{0.5}
\definecolor{green}{rgb}{0,0.5,0}


\begin{document}

\title{Towards a semantic-based representation and computation of a quantitative index for context-aware quality management in the Cloud. \\ The CloudIndex approach.}

\author{Jose Mar\'{i}a \'{A}lvarez\inst{1} \and Jos\'{e} Emilio Labra\inst{2}  \and Patricia Ordoñez de Pablos\inst{3}}


\authorrunning{Jose Mar\'{i}a Alvarez \and  Jos\'{e} Emilio Labra \and Patricia Ordoñez de Pablos}


\institute{South East European Research Center, \\ 54622, Thessaloniki, Greece\\
  \email{{jmalvarez@seerc.org}}\\
\and WESO Research Group, Department of Computer Science, University of Oviedo, \\ 33007, Oviedo, Spain.\\
  \email{{labra@uniovi.es.es}}\\  
  \and WESO Research Group, Department of Business Administration, University of Oviedo, \\ 33007, Oviedo, Spain.\\
  \email{{patriop@uniovi.es.es}}\\  
}


\date{}

\maketitle

\renewcommand{\labelitemi}{$\bullet$}

\begin{abstract}
Cloud Computing and Service Oriented Architectures have seen a dramatic increase of the amount of applications, services, 
management platforms, data, etc. gaining momentum in Information and Communication Technology and 
more specifically in the deployment of the next Internet of Services. Furthermore one of the next big things 
in a service environment lies in the creation of brokerage services that can automatically 
detect and make decisions according to an user profile, service level agreements (SLAs), etc. In this sense Quality of Service (QoS) 
seeks for providing an intelligent environment of self-management components based on domain 
knowledge in which both functional and non-functional properties of cloud components can be optimized 
in terms of cost, efficiency or reliability easing the transition to a smart cloud environment. 
Thus the creation of a QoS-based brokerage service can be seen as a special kind of policy-making strategy 
that must compile several key performance indicators (KPIs) to summarize data and information and obtain an objective quantitative measure. 
Nevertheless the quantitative analysis of several KPIs is becoming a challenging task due to a tangled and heterogeneous environment of data, providers, etc. 
In this sense existing tools and techniques based on traditional processes are preventing a proper use of the new dynamic and data environment avoiding 
more timely, adaptable and flexible (on-demand) quantitative index creation and, as a consequence, more accurate decisions. 
On the other hand, semantic-based technologies emerge to provide the adequate building blocks 
to represent domain-knowledge and process data in a flexible fashion using a common and shared data model. That is why the present paper introduces 
a Resource Description Framework (RDF) vocabulary to semantically represent and compute quantitative indexes over a real-time architecture with the aim 
of providing a context-aware system to manage QoS for brokerage services. A first qualitative evaluation and discussion of this approach 
are also presented to finally outline some conclusions and future work.
\end{abstract}
% 
% \section{Introduction}
% \input{sections/sect-intro}
% \section{Background}
% % \input{sections/sect-background}
% \section{Related Work}
% \input{sections/sect-related-work}
% \section{Semantic modeling of a quantitative composite index}
% \input{sections/sect-theoretical-rdfindex}
% \section{The CloudIndex approach}
% % \input{sections/sect-cloud-index}
% \section{An architecture for real-time computation of the CloudIndex}
% % \input{sections/sect-lambda}
% \section{Evaluation and Discussion}
% % \input{sections/sect-discussion}
% \section{Conclusions and Future Work}
% % \input{sections/sect-conclusions}

\section{Acknowledgements}
This work is part of the FP7 Marie Curie Initial Training Network ``RELATE'' (cod. 264840) and developed in the context 
of the Workpackage 4 and more specifically under the project ``Quality Management in Service-based Systems and Cloud Applications''. It is 
also supported by the ROCAS project (cod. TIN2011-27871), a research project partially funded by the Spanish Ministry of Science and Innovation.

\clearpage
\nocite{*}
\bibliographystyle{plain}
% %\bibliographystyle{unsrt}
% % %\bibliographystyle{acm}
%\bibliography{references}
\bibliography{cloud-references}
 % \renewcommand{\bibname}{References}

\end{document}

